\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-20 paper.tex
revise motivation

\subsection{A simple motivating example for $\mathsf{TEDAT}$}
Now we use a simple example to illustrate why existing traffic engineering algorithms cannot 
meet the heterogeneous bandwidth availability demands well. The toy topology we use is depicted 
in Figure \ref{motivatio_fig}(a), where there are 4 data centers and the links connecting them 
are annotated with their corresponding capacities and failure probabilities. Suppose we have two 
bandwidth demands for inter-DC transfer from DC1 to DC4, i.e., user1 (red) requires 6Gbps bandwidth 
with at least 99\% availability, and user2 (blue) requires 12Gbps bandwidth with at least 90\% availability. 
There are two paths from DC1 to DC4, i.e., DC1$\to$ DC2 $\to$ DC4, and DC1 $\to$ DC3 $\to$ DC4, whose available probabilities are $(1-4\%) \times (1-0.0001\%)=95.999904\%$ and $(1-0.1\%) \times (1-0.0001\%) = 99.8999001\%$, respectively. We apply FFC \cite{FFC} and TEAVAR \cite{Teavar}, two latest WAN traffic engineering schemes that take network failures into account, to this scenario.

>>>>

\subsection{A motivating example for $\mathsf{TEDAT}$}
Now we use a simple example to illustrate why existing traffic engineering algorithms cannot 
meet the heterogeneous bandwidth availability demands well. The toy topology we use is depicted 
in Figure \ref{motivatio_fig}(a), where there are 4 data centers and the links connecting them 
are annotated with their corresponding capacities and failure probabilities. Suppose we have two 
bandwidth demands for inter-DC transfer from DC1 to DC4, i.e., user1 (red) requires 6Gbps bandwidth 
with at least 99\% availability, and user2 (blue) requires 12Gbps bandwidth with at least 90\% availability. 
There are two paths from DC1 to DC4, i.e., DC1$\to$ DC2 $\to$ DC4, and DC1 $\to$ DC3 $\to$ DC4, whose available probabilities are $(1-4\%) \times (1-0.0001\%)=95.999904\%$ and $(1-0.1\%) \times (1-0.0001\%) = 99.8999001\%$, respectively. We apply FFC \cite{FFC} and TEAVAR \cite{Teavar}, two latest WAN traffic engineering schemes that take network failures into account, to this scenario.
